---
output: github_document
---

## Overview
`rsurv` is a lightweight package with minimal dependencies for randomly generating survival times efficiently and flexibly. Survival times can be randomly drawn from any survival distribution and all code is vectorized so that each individual can have their own survival function. Monte Carlo simulation studies that aim to simulate realistic data generating processes based on empirical data are an intended use case.

## Installation
The package can be  installed from GitHub with:

``` r
devtools::install_github("dincerti/rsurv")
```

## Usage
Survival times can be randomly drawn from arbitrary survival curves using the `rsurv()` function. Survival curves for multiple individuals are stored in objects of class `survival_curves`, which are just data frames in the format shown here:

```{r}
library("rsurv")
sc <- example_survival_curves(n = 1000)
head(sc)
```

Random survival times for each individual can then be easily drawn:

```{r}
sim <- rsurv(sc)
length(sim)
summary(sim)
```